Decoding Toronto's Crime Patterns

### 2024-01-25 outputs/paper/paper.qmd
Correct the working directory path
Update

---
title: "Decoding Toronto's Crime Patterns: A Comprehensive Analysis of Victims and Trends (2014-2022)"
author: "Chay Park"
date: today
date-format: long
bibliography: references.bib
abstract: In the period from 2014 to 2022, including the global Novel Coronavirus pandemic in 2019, this paper scrutinizes the Toronto Police annual statistical report on victims of crimes. Analyzing this extensive dataset reveals a correlation between the pandemic and crime rates, emphasizing broader trends in the top three crimes across different age groups. The findings underscore the nuanced relationship between external events, law enforcement, and crime reporting, offering insights into the complex interplay between specific events and crime statistics. This research contributes to a comprehensive understanding of societal dynamics, highlighting the potential impact of the pandemic on both crime rates and the reporting of victims of crimes over the years.
format: pdf
editor: visual
prefer-html: true
toc: true
toc-depth: 3
toc-title: Contents
number-sections: true
number-depth: 3
---

∗Code and data supporting this analysis is available at:

<https://github.com/Chay-HyunminPark/Toronto_CrimeVictims.git>[^1].

[^1]: View the repository on GitHub.

...

@@

# Load the csv file
cleaned_data <- read_csv(file = here::here("Toronto_Victims_of_Crimes/inputs/data/cleaned_data.csv"))

@@

# Load the csv file
cleaned_data <- read_csv(file = here::here("Toronto_Victims_of_Crimes/inputs/data/cleaned_data.csv"))

>>>>

---
title: "Decoding Toronto's Crime Patterns"
subtitle: "A Comprehensive Analysis of Victims and Trends (2014-2022)"
author: "Chay Park"
date: today
date-format: long
abstract: "In the period from 2014 to 2022, including the global Novel Coronavirus pandemic in 2019, this paper scrutinizes the Toronto Police annual statistical report on victims of crimes. Analyzing this extensive dataset reveals a correlation between the pandemic and crime rates, emphasizing broader trends in the top three crimes across different age groups. The findings underscore the nuanced relationship between external events, law enforcement, and crime reporting, offering insights into the complex interplay between specific events and crime statistics. This research contributes to a comprehensive understanding of societal dynamics, highlighting the potential impact of the pandemic on both crime rates and the reporting of victims of crimes over the years."
format: pdf
editor: visual
prefer-html: true
toc: true
toc-depth: 3
toc-title: Contents
thanks: "Code and data are available at: https://github.com/Chay-HyunminPark/Toronto_CrimeVictims."
number-sections: true
number-depth: 3
bibliography: references.bib
---

@@

# Set seed for reproducibility
set.seed(123)

# Load the csv file
cleaned_data <- read_csv(file = here::here("inputs/data/cleaned_data.csv"))

@@

# Load the csv file
cleaned_data <- read_csv(file = here::here("inputs/data/cleaned_data.csv"))
